---
title: "Report"
author: ""
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: yeti
    highlight: textmate
    toc: true
    toc_float: true
    toc_depth: 5
  # prettydoc::html_pretty:
  # rmdformats::html_docco:
  #   highlight: github
  #   theme: architect
  pdf_document: default
params:
  x: NA
  date_pred: NA
---

```{r setup, include=FALSE, out.width = '80%'}
knitr::opts_chunk$set(echo = TRUE)
```


# Plots


## How to

* occupancy map of the landscape where you sampled your species, in ASCII format
* the corresponding coordinates of your sampling points in CSV
  + The csv must be formatted like:
    ```{r csv format, echo=F}
    knitr::kable(summary(params$x))
    ```
  
Truc truc truc

```{r plotobs scale, echo=TRUE, message=FALSE, warning=FALSE}
ggplot(params$x,aes_string(x=params$date_pred))+geom_histogram()
```

# References

<script>
    $(document).ready(function() {
      $items = $('div#TOC li');
      $items.each(function(idx) {
        num_ul = $(this).parentsUntil('#TOC').length;
        $(this).css({'text-indent': num_ul * 10, 'padding-left': 0});
      });

    });
</script>


<style>
body {
text-align: justify}
</style>

